Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-30 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

The topography of a group of more than four fixed HeLa cells can be seen in 
figure~\ref{fig:SICM_STED1}Aa the corresponding slope representation in Ab, the confocal image in 
Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
a black dotted line in Aa and Ab. Many different cell topographies were visible in Aa.

A round cell with a maximum height of approximately 16.4~{\textmu}m height can be seen in the 
right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
was flat and extending (?) the scanned region (yellow arrow). A second flat but smaller cell was 
marked with a with arrow ending with a white dot. Marked with a purple arrow ending with a purple
dot was a small and a kind of roundish cells. This cell besitzt (german)
a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
The protrusion was approximately 4~{\textmu}m long and 5~{\textmu}m high (Dc, 
\cite{Hagemann2018}).

Beside the different topographies of these two cells, they also display different types of actin 
fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
fibres (yellow arrowheads).

>>>>

The topography of a group of more than four fixed HeLa cells can be seen in 
figure~\ref{fig:SICM_STED1}Aa the corresponding slope representation in Ab, the confocal image in 
Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
a black dotted line in Aa and Ab. C is showing the arrangement of the SICM image (yellow 
rectangle) against the confocal/STED image (gray rectangle). Many different cell topographies were
visible in Aa.

A round cell with a maximum height of approximately 16.4~{\textmu}m height can be seen in the 
right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
was flat and exceeding the scanned region (yellow arrow). A second flat but smaller cell was 
marked with a white arrow, which was ending with a white dot. Marked with an orange arrow (Aa, Ab) 
respectively with a cyan arrow (Ba, Bb) was a small, kind of roundish cells. This cell posesses 
a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
The protrusion was approximately 4~{\textmu}m long and 5~{\textmu}m high (Dc, 
\cite{Hagemann2018}).

Beside the different topographies of these two cells, they also display different types of actin 
fibers. In the inside of the first mentioned round cell nearly no actin signal could be detected 
(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
fibers (yellow arrowheads). The cell marked with the white arrow, which was ending with a white 
dot, could be just seen half in the confocal/STED images and dot-like actin structures 
predominate. The cell with the protrusion was showing fan-like actin structures (cyan arrow, which
was ending with a cyan dot and white arrow, which was ending with a white dot) where the cell was
connected to surrounding cells and actin agglomerations (cyan arrow). The agglomerations turned 
out to be \emph{rings} by watching the STED image (cyan circle). Such a structure could be also 
found in the protrusion (white arrowhead, Df and Dg). In the center of the \emph{actin ring} two 
dots could be identified (black arrowheads, Da).

Structures that would have been missed, if just one single technique alone would have been used: 
\textsf{
\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
\label{tab:missing_structures}
What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
The connections between the small round cell with the protrusion and the other cells & \textbf{PARTLY} & YES \\ \hline
The full extent of the protrusion & YES & \textbf{NO} \\ \hline
The connection between the roundish and the flat cell & \textbf{NO} & YES \\
\end{tabular}}

This points out again one of the biggest advantage of correlative microscopy: making things 
visible, that were invisible to one of the microscopy techniques alone. This could be due to 
fluorescence signals that were out of focus $-$ this could be the case by the actin signal that
suddenly ends in the protrusion $-$ (STED microscopy) or due to overhanging membranes $-$ this 
could be the case by the connections between the cells (especially between the highest and the
flat cell) $-$ (SICM) (Quelle).
